Response to reviewers

### 2025-01-29 Manuscript/ecography_reponse_letter_2.tex
highligthed todos

\textit{Our results show that the loss of  functional diversity for several metrics was not more than expected by chance.
This could be due to the taxonomic distribution of the extinct birds: this example data has approximatively $58$\% passerines while the majority of anthropogenic extinctions have been affecting non-passerines (approximatively $75$\%).
These species tend to be larger and possess more unique morphological traits (thus resulting in relatively large reductions in functional diversity).} Lines 431-436. %@@@

>>>>

\textit{Our results show that the loss of  functional diversity for several metrics was not more than expected by chance.
This could be due to the taxonomic distribution of the extinct birds: these Hawaiian data comprise approximatively $58$\% passerines while the majority of anthropogenic extinctions have involved non-passerines (approximatively $75$\%).
Non-passerines tend to be larger and possess more unique morphological traits (thus resulting in relatively large reductions in functional diversity).} Lines 431-436. %@@@
